\thispagestyle{empty}
\begin{titlepage}
{\bf\Large Acknowledgements}\\

There are so many people that I would like to thank, each one helped me
with their own special way. 

First of all, I would like to thank my co-advisor
Professor Kostas Magoutis for guiding and having trust in
this work, but mainly I would like to thank him for his continuous enthusiasm and willingness to
help me at every stage of this thesis. I would also like to thank my advisor Professor Manolis Katevenis.

I want to acknowledge Antonis Papaioannou, Emmanouil Papoutsakis, members of PaaSage team for their valuable feedback on my work as well as Maria Korozi, Asterios Leonidis and Stavroula Ntoa for the collaboration during the jisa journal publication and the design of the user interface.

I need to express my gratitude to the University of Crete and the Department
of Computer Science; as well as the Institute of Computer Science of the Foundation for Research and
Technology for supporting me.

During my time in Heraklion, I have been fortunate to enjoy the friendship
of a number of special people. I would like to give my appreciation to
my friends, Theodoros Sfakianakis, John Bikouvarakis, Christos Mousamatas and Apostolis Matthaiakis for the encouragement and the support during my undergraduate and graduate studies as well as for the great
moments we had together during these years.

I would also thank to my partner, Natalia Athanasiadi, for all her love, support, patience and encouragement. It was her continied encouragement that got me through this process.

\bigskip

This thesis is dedicated to the memory of my mother Chariklia Lagourani who passed away in 2015 at the age of 63. She passed away just two months before this thesis was finished and at the last of her days she was proud of my achievements in completing my master's thesis.

\begin{flushright}Christos Papoulas\end{flushright}
\vfill
\end{titlepage}
